New lower bounds for Schur and weak Schur numbers \thanks{Submitted to the editors 02/24/2022.}

### 2022-02-24 article/soumission_SIAM/article.tex
remarque rowley

\documentclass[final,onefignum,onetabnum]{siamart190516}

@@

Here \(n\) can be seen as a "special" color in the sense that it is not constrained by Assertion (\ref{eq:constemp}).
However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.

@@

Note that the special color \(n\) is not necessarily the last color by order of appearance, any color can play this role.
Now, we introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.

>>>>

\documentclass[review,onefignum,onetabnum]{siamart190516}

@@

Here \(n\) can be seen as a "special" color in the sense that it is not constrained by Assertion (\ref{eq:constemp}).
Number \(p\) is necessarily colored with color \(n\). However, note that \(n\) is not necessarily the last color by order of appearance.

@@

Number \(a\) is necessarily colored with color \(n\). Note that the special color \(n\) is not necessarily the last color by order of appearance.
Now, we introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
